### 2015-07-30 Docs/runtime_parameters/runtime_parameters.tex
updated parameters

\rowcolor{tableShade}
\verb=  burner_threshold_cutoff  = &   Mass fraction cutoff for burner\_threshold\_species  used in burner threshold  &  1.d-10 \\
\verb=  burner_threshold_species  = &   Name of the species to be used in burner threshold  &  "" \\
\rowcolor{tableShade}
\verb=  do_burning  = &   turn on (.true.) or off (.false.) burning  &  .true. \\
\verb=  do_subgrid_burning  = &   break a zone into subzones, call the burner in each subzone and then average the result to the original cell  &  .false. \\

@@

\verb=  the_copy_cache_max  = &    Number of boxassoc layouts we keep in memory to avoid having to recompute the boxassoc, which is computationally expensive.  &  25 \\

@@

@@

@@

\rowcolor{tableShade}
\verb=  check_base_name  = &   prefix to use in checkpoint file names  &  "chk" \\
\verb=  chk_int  = &   Number of timesteps between writing a checkpoint file  &  0 \\
\rowcolor{tableShade}
\verb=  diag_buf_size  = &   number of timesteps to buffer diagnostic output information before writing (note: not implemented for all problems)  &  10 \\
\verb=  lUsingNFiles  = &   If .true., use nOutFiles processors to write checkpoint and plotfiles. Fortran has the unfortunate feature of each processor only being able to write out 1-2GB each without crashing.  &  .true. \\
\rowcolor{tableShade}
\verb=  nOutFiles  = &   If lUsingNFiles = .true., use this many processors to write checkpoint and plotfiles.  Fortran has the unfortunate feature of each processor only being able to write out 1-2GB each without crashing.  &  64 \\
\verb=  plot_Hext  = &   plot external heating (Hext) in plotfile  &  .false. \\
\rowcolor{tableShade}
\verb=  plot_Hnuc  = &   plot nuclear energy generation rate (Hnuc) in plotfile  &  .true. \\
\verb=  plot_ad_excess  = &   plot the adiabatic excess  &  .false. \\
\rowcolor{tableShade}
\verb=  plot_base  = &   plot w0\_x, w0\_y, w0\_z, divw0, rho0, rhoh0, h0, and p0 in plotfile  &  .false. \\
\verb=  plot_base_name  = &   prefix to use in plotfile file names  &  "plt" \\
\rowcolor{tableShade}
\verb=  plot_cs  = &   plot soundspeed  &  .false. \\
\verb=  plot_deltat  = &   rather than use a plot interval, plot a file after the solution has advanced past plot\_deltat in time  &  -1.d0 \\
\rowcolor{tableShade}
\verb=  plot_eta  = &   plot $\etarho$ in plotfile  &  .false. \\
\verb=  plot_gpi  = &   plot pi and grad(pi)  &  .true. \\
\rowcolor{tableShade}
\verb=  plot_h_with_use_tfromp  = &   Turn on storing of enthalpy-based quantities in the plotfile when we are running with {\tt use\_tfromp}  &  .true. \\
\verb=  plot_int  = &   plot interval  &  0 \\
\rowcolor{tableShade}
\verb=  plot_omegadot  = &   plot omegadot in plotfile  &  .true. \\
\verb=  plot_pidivu  = &   plot pi * div(U) -- this is a measure of conservation of energy  &  .false. \\
\rowcolor{tableShade}
\verb=  plot_processors  = &   create a field in the plotfile storing the processor number for each zone  &  .false. \\
\verb=  plot_spec  = &   plot species and omegadot in plotfile  &  .true. \\
\rowcolor{tableShade}
\verb=  plot_trac  = &   plot tracers in plotfile  &  .false. \\
\verb=  single_prec_plotfiles  = &   store the state data in single precision  &  .false. \\

@@

\rowcolor{tableShade}
\verb=  model_file  = &   input model file  &  "model.hse" \\
\verb=  perturb_model  = &   Turn on a perturbation in the initial data.  Problem specific.  &  .false. \\

>>>>

\rowcolor{tableShade}
\verb=  burner_threshold_cutoff  = &   Mass fraction cutoff for burner\_threshold\_species  used in burner threshold  &  1.d-10 \\
\verb=  burner_threshold_species  = &   Name of the species to be used in burner threshold  &  "" \\
\rowcolor{tableShade}
\verb=  do_burning  = &   turn on (.true.) or off (.false.) burning  &  .true. \\
\verb=  do_subgrid_burning  = &   break a zone into subzones, call the burner in each subzone and then average the result to the original cell  &  .false. \\
\rowcolor{tableShade}
\verb=  reaction_sum_tol  = &   mass fraction sum tolerance (if they don't sum to 1 within this tolerance, we abort)  &  1.d-10 \\

@@

\verb=  the_copy_cache_max  = &    Number of boxassoc layouts we keep in memory to avoid having to recompute the boxassoc, which is computationally expensive.  &  128 \\

@@

\verb=  the_ml_layout_strategy  = &   This prarmeter has no impact on single-level runs! 0: This uses either knapsack or sfc on each level.  Before boxes are    distributed, MPI ranks are sorted according to the memory usage by    all levels.  This is our traditional approach. 1: This uses sfc on each level.  MPI ranks are sorted according to the    memory usage by lower levels.  &  0 \\

@@

\verb=  use_tpert_in_tagging  = &   pass $T'$ into the tagging routines as the auxillary multifab instead of the default $\rho H_\mathrm{nuc}$.  &  .false. \\

@@

\rowcolor{tableShade}
\verb=  check_base_name  = &   prefix to use in checkpoint file names  &  "chk" \\
\verb=  chk_int  = &   Number of timesteps between writing a checkpoint file  &  0 \\
\rowcolor{tableShade}
\verb=  diag_buf_size  = &   number of timesteps to buffer diagnostic output information before writing (note: not implemented for all problems)  &  10 \\
\verb=  lUsingNFiles  = &   If .true., use nOutFiles processors to write checkpoint and plotfiles. Fortran has the unfortunate feature of each processor only being able to write out 1-2GB each without crashing.  &  .true. \\
\rowcolor{tableShade}
\verb=  mini_plot_base_name  = &   basename for the mini plotfiles  &  "miniplt" \\
\verb=  mini_plot_deltat  = &   rather than use a mini plot interval, output a mini plotfile every mini\_plot\_deltat in time  &  -1.d0 \\
\rowcolor{tableShade}
\verb=  mini_plot_int  = &   mini plot interval  &  -1 \\
\verb=  mini_plot_var1  = &   names of specific variables to store in the mini plotfile  &  "" \\
\rowcolor{tableShade}
\verb=  mini_plot_var2  = &    &  "" \\
\verb=  mini_plot_var3  = &    &  "" \\
\rowcolor{tableShade}
\verb=  mini_plot_var4  = &    &  "" \\
\verb=  mini_plot_var5  = &    &  "" \\
\rowcolor{tableShade}
\verb=  mini_plot_var6  = &    &  "" \\
\verb=  mini_plot_var7  = &    &  "" \\
\rowcolor{tableShade}
\verb=  mini_plot_var8  = &    &  "" \\
\verb=  mini_plot_var9  = &    &  "" \\
\rowcolor{tableShade}
\verb=  nOutFiles  = &   If lUsingNFiles = .true., use this many processors to write checkpoint and plotfiles.  Fortran has the unfortunate feature of each processor only being able to write out 1-2GB each without crashing.  &  64 \\
\verb=  plot_Hext  = &   plot external heating (Hext) in plotfile  &  .false. \\
\rowcolor{tableShade}
\verb=  plot_Hnuc  = &   plot nuclear energy generation rate (Hnuc) in plotfile  &  .true. \\
\verb=  plot_ad_excess  = &   plot the adiabatic excess  &  .false. \\
\rowcolor{tableShade}
\verb=  plot_base  = &   plot w0\_x, w0\_y, w0\_z, divw0, rho0, rhoh0, h0, and p0 in plotfile  &  .false. \\
\verb=  plot_base_name  = &   prefix to use in plotfile file names  &  "plt" \\
\rowcolor{tableShade}
\verb=  plot_cs  = &   plot soundspeed  &  .false. \\
\verb=  plot_deltat  = &   rather than use a plot interval, plot a file after the solution has advanced past plot\_deltat in time  &  -1.d0 \\
\rowcolor{tableShade}
\verb=  plot_eta  = &   plot $\etarho$ in plotfile  &  .false. \\
\verb=  plot_gpi  = &   plot pi and grad(pi)  &  .true. \\
\rowcolor{tableShade}
\verb=  plot_h_with_use_tfromp  = &   Turn on storing of enthalpy-based quantities in the plotfile when we are running with {\tt use\_tfromp}  &  .true. \\
\verb=  plot_int  = &   plot interval  &  0 \\
\rowcolor{tableShade}
\verb=  plot_omegadot  = &   plot omegadot in plotfile  &  .true. \\
\verb=  plot_pidivu  = &   plot pi * div(U) -- this is a measure of conservation of energy  &  .false. \\
\rowcolor{tableShade}
\verb=  plot_processors  = &   create a field in the plotfile storing the processor number for each zone  &  .false. \\
\verb=  plot_spec  = &   plot species and omegadot in plotfile  &  .true. \\
\rowcolor{tableShade}
\verb=  plot_trac  = &   plot tracers in plotfile  &  .false. \\
\verb=  single_prec_plotfiles  = &   store the state data in single precision  &  .false. \\

@@

\rowcolor{tableShade}
\verb=  model_file  = &   input model file  &  "model.hse" \\
\verb=  perturb_model  = &   Turn on a perturbation in the initial data.  Problem specific.  &  .false. \\
\rowcolor{tableShade}
\verb=  print_init_hse_diag  = &   print out HSE diagnostics as a function of r for the initial model  &  .false. \\
